### 2014-11-13 tex/operations.tex
Proofread opearations.tex

In the field-access rewrite rule in~\figref{fig:fHeap}(a), after the
non-nullness check, the rules gets the field type $\cfgnt{C}$ and uses
the summarize machine,\figref{fig:symInit}, to get a new summary heap
that is initialized on the field $\cfgnt{f}$. The summary heap after
initialization is further modified in the final state of the field
access to include a new stack reference pointing to the value set from
the read. The new stack reference is the return value from the operation.
\input{value-set-def}
The value set computation is local: it only considers
constraint locations on the reference $\cfgnt{r}$. Further, it only
includes things that are feasible under the current path condition
$\phi_g$. It also ensures that the access path valid.

There is a constraint from the base reference and a given
location. Once a location is selected, the field is accessed to get
another reference, and from that reference there is a set of locations
each with a constraint. The first constraint from the base reference
plus this second constraint to the actual location of the field
comprise the access path. For each member of the value set, these
constraints together with the global path constraint must be satisfied
on some aliasing assignment.

@@

Strengthening in the field write creates a value set the
contains feasible locations if the write happens on that location (the
first call) and feasible locations if the write does not happen on
that location (the second call). This is the conditional in the write. In the case that $\phi$ is true
then $\cfgnt{r}_\mathit{cur}$ will point to the constraint location pairs of
$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will continue
to point to the constraint location pair it is currently referenced.
As the references are immutable, the rule creates fresh reference for
each $\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value sets.

@@

We use the three sets of constraints to update the current global heap
constraint $\phi_g$ and create a new global heap constraint
$\phi_g^\prime$. We add to $\phi_g$ the disjunction of the constraints
in $\Phi_\alpha$ to indicate that if any of the constraints are
satisfiable, then references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ can be
equal. Furthermore, we had to the global heap constraint,
$\phi_g^\prime$, the conjunctions of negations to the constraints in
$\Phi_0$ and $\Phi_1$. This indicates for locations that are not
common to the references, the negations of their constraints are
satisfiable. The rule does not complete (i.e., is not feasible) if the new global constraint is not satisfied on any aliasing assignment. In such a case, the true outcome is not possible on any heap in the summary.

Before the rewrite rule returns true we check the
satisfiability of the updated global heap constraint.

Consider the example in~\figref{fig:initHeap}(c). In order to to check
if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
pairs associated with each of the references:
\[
\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
\]
\[
\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
\]
\noindent{The three constraint sets are:} 
\[
\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
\]
\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
\]
\noindent{The equals references-false is the logical dual of the
  reference-true rewrite rule. The references-false is also shown
  in~\figref{fig:eqs}.}

>>>>

In the field-access rewrite rule in~\figref{fig:fHeap}(a), after the
null check, the rule gets the field type $\cfgnt{C}$ and uses
the summarize machine, \figref{fig:symInit}, to get a new summary heap
that is initialized on the field $\cfgnt{f}$. After
initialization, the summary heap is further modified to include 
a new stack reference pointing to the value set from
the read. The new stack reference is the return value from the operation.
\input{value-set-def}
The value set computation is local: it only considers
constraint locations on the reference $\cfgnt{r}$. Further, it only
includes things that are feasible under the current path condition
$\phi_g$. It also ensures that the access path valid.

There is a constraint $\phi$ from the base reference $r$ and a given
location. Once a location $l$ is selected, the field $\cfgnt{f}$ is accessed to get
another reference $r^\prime$, and from that reference there is a set of locations
each with a constraint. The first constraint $\phi$ from the base reference
plus this second constraint to the actual location of the field $\phi^\prime$
comprise the access path. For each member of the value set, these
constraints together with the global path constraint must be satisfied
on some aliasing assignment.

@@

Strengthening in the field write creates a value set that
contains two types of locations:  those for the case where the write is feasible (the
first call), and those for the case where it is not (the second call). 
This is the conditional in the write. In the case that $\phi$ is true
then $\cfgnt{r}_\mathit{cur}$ will point to the constraint location pairs of
$\cfgnt{L}(\cfgnt{r})$ while if $\phi$ is false then $\cfgnt{r}_\mathit{cur}$ will continue
to point to the constraint location pair it is currently referenced.
As the references are immutable, the rule creates fresh references for
each $\cfgnt{r}_\mathit{cur}$ and points them to the appropriate value sets.

@@

We use the three sets of constraints to update the current global heap
constraint $\phi_g$ and create a new global heap constraint
$\phi_g^\prime$. We add to $\phi_g$ the disjunction of the constraints
in $\Phi_\alpha$ to indicate that if any of the constraints are
satisfiable, then references $\cfgnt{r}_0$ and $\cfgnt{r}_1$ can be
equal. Furthermore, we conjoin to the global heap constraint 
$\phi_g^\prime$, the conjunctions of negations to the constraints in
$\Phi_0$ and $\Phi_1$. This indicates for locations that are not
common to the references, the negations of their constraints are
satisfiable. The rule does not complete (i.e., is not feasible) if the new
 global constraint is not satisfied on any aliasing assignment. In such a case, 
 the $\cfgt{true}$ outcome is not possible on any heap in the summary.

Before the rewrite rule returns $\cfgt{true}$ we check the
satisfiability of the updated global heap constraint.

Consider the example in~\figref{fig:initHeap}(c). In order to to check
if $\cfgnt{r}_1^i$ and $\cfgnt{r}_2^i$ are equal we first get the constraint location
pairs associated with each of the references:
\[
\cfgnt{L}(\cfgnt{r}_1^i) = \{ (\phi_{1a}\; \cfgnt{l}_\mathit{null})\; (\phi_{1b}\; \cfgnt{l}_1) \} 
\]
\[
\cfgnt{L}(\cfgnt{r}_2^i) = \{ (\phi_{2a}\; \cfgnt{l}_\mathit{null})\; (\phi_{2b}\; \cfgnt{l}_2)\; (\phi_{2c}\; \cfgnt{l}_1) \} \\
\]
\noindent{The three constraint sets are:} 
\[
\Phi_\alpha = \{ (\phi_{1a}\; \wedge\; \phi_{2a} ) (\phi_{1b}\; \wedge\; \phi_{2c} ) \}\;
\Phi_0 = \{ \}\; \Phi_1 = \{ \phi_{2b}\} \\
\]
\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
\]
\noindent{The equals references-false rule is the logical dual of the
  reference-true rewrite rule. The references-false rule is also shown
  in~\figref{fig:eqs}.}
